A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Reshaping data for graphs

ips.data <- data.frame(Experiment=character(),                      
                       PUTs=character(),
                       reboots=character())

ips.aggregates <- data.frame(Experiment=character(),
                             PUTs = character(),
                             reboots = character(),
                             avgPUTs = character(),
                             avgreboots = character() )

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-reboots-cache=32-",i,".csv"))
    ips.data <- rbind(ips.data,
                      data.frame(Experiment=rep(i,length(this.data$PUTs)),
                                 PUTs=as.integer(this.data$PUTs),
                                 reboots=as.integer(this.data$reboots))
                       )

    ips.aggregates <- rbind( ips.aggregates,
                            data.frame(Experiment=i,
                                       PUTs = median(this.data$PUTs),
                                       reboots = median(this.data$reboots),
                                       avgPUTs = mean(this.data$PUTs),
                                       avgreboots = mean(this.data$reboots) )
                            )
}
@

>>>>

ips.data <- data.frame(Experiment=character(),                      
                       PUTs=character(),
                       reboots=character(),
                       idu=character(),
                       idx=character())

ips.aggregates <- data.frame(Experiment=character(),
                             PUTs = character(),
                             reboots = character(),
                             avgPUTs = character(),
                             avgreboots = character(),
                             totalIPs = character())

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-reboots-cache=32-",i,".csv"))
    this.len <- length(this.data$PUTs)
    seq <- 1:this.len
    ips.data <- rbind(ips.data,
                      data.frame(Experiment=rep(i,length(this.data$PUTs)),
                                 idu=seq,
                                 idx=seq/this.len,
                                 PUTs=as.integer(this.data$PUTs),
                                 reboots=as.integer(this.data$reboots))
                       )

    ips.aggregates <- rbind( ips.aggregates,
                            data.frame(Experiment=i,
                                       PUTs = median(this.data$PUTs),
                                       reboots = median(this.data$reboots),
                                       avgPUTs = mean(this.data$PUTs),
                                       avgreboots = mean(this.data$reboots),
                                       totalIPs =this.len )
                            )
}
@
